Appendix 4: example of index standardization of fishery-independent survey data with inlabru

### 2022-03-17 doc/appendix-pcod-inlabru.Rmd
use correct inla mesh
1->2

This model will attempt to replicate the model fit in Appendix 1 as an example of how index standardization can also be achieved with inlabru. 
Once again we will use a data set built into the package: trawl survey data for Pacific Cod in Queen Charlotte Sound.
The density units are kg/km^2^. 
This can be converted to tonnes per km2 by dividing by 1000, which can sometimes scale better.

@@

spde <- inla.spde2.pcmatern(
  mesh = mesh$mesh,
  prior.range = c(10, 0.05), # P(range < 10) = 0.05
  prior.sigma = c(2, 0.05) # P(sigma > 2) = 0.05
) 
```

>>>>

This model will attempt to replicate the model fit in Appendix 2 as an example of how index standardization can also be achieved with inlabru. 
Once again we will use a data set built into the package: trawl survey data for Pacific Cod in Queen Charlotte Sound.
The density units are kg/km^2^. 
This can be converted to tonnes per km2 by dividing by 1000, which can sometimes scale better.

@@

spde <- inla.spde2.pcmatern(
  mesh = inla_mesh,
  prior.range = c(10, 0.05), # P(range < 10) = 0.05
  prior.sigma = c(2, 0.05) # P(sigma > 2) = 0.05
) 
```
